BLAST: Block Applications for Things

### 2022-03-02 demo-eswc22/paper.tex
added notes

To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction over devices communicating with Bluetooth Low Energy and USB HID.
We also provide access to online APIs related to speech input and output.

@@

>>>>

To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction over devices communicating with Bluetooth Low Energy and USB Human Interface Device (HID) Class.
We also provide access to online APIs related to speech input and output.

@@

@@@Web Bluetooth has certain restrictions (security, reading RSSI), server should not have these restrictions.
